Projecting Global Filesystems into Local Containers for High-throughput Computing on HPC Resources

### 2019-01-17 paper.tex
Updated style to ACM sigconf

\documentclass[conference]{IEEEtran}

@@

@@

\author{
\IEEEauthorblockN{Tim Shaffer}
\IEEEauthorblockA{University of Notre Dame \\
Notre Dame, Indiana 46556 \\
tshaffe1@nd.edu}
\and
\IEEEauthorblockN{Nicholas Hazekamp}
\IEEEauthorblockA{University of Notre Dame \\
Notre Dame, Indiana 46556 \\
nhazekam@nd.edu}
\and
\IEEEauthorblockN{Jakob Blomer}
\and
\IEEEauthorblockN{Douglas Thain}
\IEEEauthorblockA{University of Notre Dame \\
Notre Dame, Indiana 46556 \\
dthain@nd.edu}
}

>>>>

\documentclass[sigconf]{acmart}

@@

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[HPDC '19]{HPDC '19: International ACM Symposium on High-Performance Parallel and Distributed Computing}{June 24--28, 2019}{Phoenix, AZ}

@@

\author{Tim Shaffer}
\email{tshaffe1@nd.edu}
\orcid{}
\affiliation{%
  \institution{University of Notre Dame}
  \city{Notre Dame}
  \state{Indiana}
  \postcode{46556}
}

\author{Nicholas Hazekamp}
\email{nhazekam@nd.edu}
\orcid{}
\affiliation{%
  \institution{University of Notre Dame}
  \city{Notre Dame}
  \state{Indiana}
  \postcode{46556}
}

\author{Jakob Blomer}
\email{jblomer@cern.ch}
\orcid{}
\affiliation{%
  \institution{CERN}
  \city{Geneva}
  \country{Switzerland}
}

\author{Douglas Thain}
\email{dthain@nd.edu}
\orcid{}
\affiliation{%
  \institution{University of Notre Dame}
  \city{Notre Dame}
  \state{Indiana}
  \postcode{46556}
}

\renewcommand{\shortauthors}{Shaffer et al.}

%
% The CCSXML code is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code.
%

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{global filesystem}
